Using Deep Learning to Identify Patients with Cognitive Impairment in Electronic Health Records

### 2021-11-12 Submission/Paper/ML4H/Paper.tex
in the middle of getting ready for arXiv
more errors fixed...
9 more errors left...
FIXED ALL THE ERRORS THANK GOD

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{tabto}    
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{float}
\usepackage{natbib}
\usepackage{url}

@@

\begin{table}[htb]
\floatconts
{tab:table1}
{\caption{Demographics of Data}}
\resizebox{\columnwidth}{}{%
\begin{tabular}{lccc}
        \toprule
        \bfseries Characteristic & \bfseries (N = 16428) \\
        \midrule
        \textbf{Age (years) mean (SD)} & \fseries 73.01 (7.96) \\ 
        \textbf{Gender Male, \emph n (\%)}  & \fseries 8740 (53.2)\\ 
        \textbf{Race, \emph n (\%)} \\ 
            \hspace{10mm} White & 14896 (90.7) \\
            \hspace{10mm} Other/Not Recorded & 608 (3.7) \\
            \hspace{10mm} Black & 570 (3.5) \\
            \hspace{10mm} Hispanic & 170 (1.0) \\
            \hspace{10mm} Asian & 168 (1.0) \\
            \hspace{10mm} Indigenous & 16 (0.01) \\
        \textbf{\textit{APOE} Genotype, \emph n (\%)} \\ 
            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$2 & 2028 (12.3)} \\
            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$3 & 10177 (62.0)} \\
            \hspace{10mm} {\textit{APOE} ${\bm{\varepsilon}}$4 & 4223 (25.7)} \\
        \textbf{Average Speciality Visits (SD)} & 1.67 (4.6) \\ 
        \textbf{Average PCP Encounters (SD)} &  5.25 (5.63) \\ 
        % \textbf{Encounters AVG (SD)} & 14.55 (23.2) \\
        % \textbf{Keyword Matches AVG (SD)} & 26 (54.03) \\
        \bottomrule
\end{tabular}
}
\end{table}

@@

\includegraphics[width=.75\linewidth]{UMAP Figure 2 Final.png}
}
\end{figure}

@@

    \toprule 
    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries M/I (\%) \\ 
    \midrule
    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.17 & \fseries 0.83 & \fseries 0.11  \\
    \bfseries{\textit{APOE} ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.21 & \fseries 0.79 & \fseries 0.17  \\

    \bottomrule
  \end{tabular}} 
}

@@

\begin{figure}[htb]
\caption{Confusion Matrix Patient Level Prediction Counts for ClinicalBERT}
\resizebox{\columnwidth}{!}{%
\label{fig:fig2}
\centering 
\includegraphics[scale=0.5]{Confusion Matrix Figure 3.png}

@@

% Appendix A
% Figure 2 - Overview
\section{Overview}
\begin{figure}[h] \label{app:overview}
\centering 
\includegraphics[scale = 0.60]{APOE SLAT Overview High Resolution.png}
\caption{Overview}

@@

% Appendix D
\section{Keywords} 
\begin{table}[hbtp] 
\floatconts
{app:keywords}
    {\begin{tabular}{lccc}
        \toprule
        \bfseries Keyword & \bfseries Match Count\\
        \midrule

        \textbf{Memory} & \fseries 109218 \\ 
        \textbf{Cognition}  & \fseries 87655 \\ 
        \textbf{Dementia} & \fseries 51034 \\ 
        \textbf{Cerebral} & \fseries 45886 \\ 
        \textbf{Cerebrovascular} & \fseries 36370 \\ 
        \textbf{Cerebellar} & \fseries 26863 \\
        \textbf{Cognitive Impairment} & \fseries 20267 \\ 
        \textbf{Alzheimer} & \fseries 20581 \\ 
        \textbf{MOCA} & \fseries 9767 \\ 
        \textbf{Neurocognitive} & \fseries 7711 \\ 
        \textbf{MCI} & \fseries 3889 \\ 
        \textbf{Amnesia} & \fseries 3695 \\ 
        \textbf{AD} & \fseries 2673 \\ 
        \textbf{Lewy} & \fseries 2561 \\ 
        \textbf{MMSE} & \fseries 2134 \\ 
        \textbf{LBD} & \fseries 224 \\ 
        \textbf{Corticobasal} & \fseries 147 \\ 
        \textbf{Pick's} & \fseries 41 \\

        \bottomrule
        \end{tabular}}
        {\caption{Keywords indicative of Cognitive Impairment}} \\
\end{table}

% Appendix E
\section{Top TF-IDF Word Features} \label{app:app3}
\begin{table}[hbtp]
    {\begin{tabular}{cccc}
    \toprule 
    \bfseries Word & \bfseries Corr & \bfseries Word & \bfseries Corr &
    \midrule

    \textbf{Intact} & \fseries 0.56 & \textbf{Experiences} & \fseries 0.36 \\
    \textbf{Oriented} & \fseries 0.43 & \textbf{Associations} & \fseries 0.36 \\ 
    \textbf{Concentration} & \fseries 0.42 & \textbf{Homicidal} & \fseries 0.36 \\ 
    \textbf{Orientation} & \fseries 0.41 & \textbf{Observation} & \fseries 0.36 \\
    \textbf{Sensorium} & \fseries 0.40 & \textbf{Knowledge} & \fseries 0.36 \\ 
    \textbf{Perceptions} & \fseries 0.40 & \textbf{Abstract} & \fseries 0.36 \\
    \textbf{Judgement} & \fseries 0.39 & \textbf{Suicidal} & \fseries 0.35 \\
    \textbf{Fund} & \fseries 0.38 & \textbf{Attention} & \fseries 0.35 \\
    \textbf{Insight } & \fseries 0.36 & \textbf{Content} & \fseries 0.34 \\ 
    \textbf{Ideation} & \fseries 0.36 & \textbf{Thought} & \fseries 0.34  \\

    \bottomrule
  \end{tabular}}
  {\caption{Top 20 TF-IDF Word Features and their Correlation Coefficient}}
\end{table}

@@

% Table 3 + 4 - Relation of Med/ICD Codes to Model Predictions
% \begin{table*}[hbtp]
% \floatconts
% {tab:table3}
% \centering 
%   {\begin{tabular}{cccccc}
%     \toprule 
%     \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%)  \\ 
%     \midrule
%     \bfseries{APOE ${\bm{\varepsilon}}$2} & \fseries 1754 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
%     \bfseries{APOE ${\bm{\varepsilon}}$3} & \fseries 8751 & \fseries 0.15 & \fseries 0.85 & \fseries 0.11  \\
%     \bfseries{APOE ${\bm{\varepsilon}}$4} & \fseries 3436 & \fseries 0.18 & \fseries 0.82 & \fseries 0.17  \\

>>>>

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{tabto}    
\usepackage{bm}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{float}
\usepackage{natbib}
\usepackage{url}
\usepackage{textcomp}
% \usepackage{syntonly}
% \syntaxonly

@@

\begin{table}[htb]
\floatconts
{tab:table1}
{\caption{Demographics of Data}}
\centering
\resizebox{\columnwidth}{!}{
        \begin{tabular}{lccc}
            \toprule
            \bfseries Characteristic & \bfseries (N = 16428) \\
            \midrule
            \bfseries Age (years) mean (SD) & 73.01 (7.96) \\ 
            \bfseries Gender Male, \emph n (\%) & 8740 (53.2)\\ 
            \bfseries Race, \emph n (\%) \\ 
                \hspace{10mm} White & 14896 (90.7) \\
                \hspace{10mm} Other/Not Recorded & 608 (3.7) \\
                \hspace{10mm} Black & 570 (3.5) \\
                \hspace{10mm} Hispanic & 170 (1.0) \\
                \hspace{10mm} Asian & 168 (1.0) \\
                \hspace{10mm} Indigenous & 16 (0.01) \\
            \bfseries \textit{APOE} Genotype, \emph n (\%) \\ 
                \hspace{10mm} \textit{APOE} ${\bm{\varepsilon}}$2 & 2028 (12.3) \\
                \hspace{10mm} \textit{APOE} ${\bm{\varepsilon}}$3 & 10177 (62.0) \\
                \hspace{10mm} \textit{APOE} ${\bm{\varepsilon}}$4 & 4223 (25.7) \\
            \bfseries Average Speciality Visits (SD) & 1.67 (4.6) \\ 
            \bfseries Average PCP Encounters (SD) &  5.25 (5.63) \\ 
            % \bfseriesEncounters AVG (SD)} & 14.55 (23.2) \\
            % \bfseriesKeyword Matches AVG (SD)} & 26 (54.03) \\
            \bottomrule
        \end{tabular}
}
\end{table}

@@

\includegraphics[width=.75\linewidth]{UMAP_Figure_2_Final.png}
}
\end{figure}

@@

    \toprule 
    \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries M/I (\%) \\ 
    \midrule
    \bfseries \textit{APOE} ${\bm{\varepsilon}}$2 & 1754 & 0.17 & 0.83 & 0.11  \\
    \bfseries \textit{APOE} ${\bm{\varepsilon}}$3 & 8751 & 0.17 & 0.83 & 0.11  \\
    \bfseries \textit{APOE} ${\bm{\varepsilon}}$4 & 3436 & 0.21 & 0.79 & 0.17  \\

    \bottomrule
  \end{tabular}
}

}

@@

\begin{figure}[htb]
\caption{Confusion Matrix Patient Level Prediction Counts for ClinicalBERT}
\resizebox{\columnwidth}{!}{%
\label{fig:fig2}
\centering 
\includegraphics[scale=0.5]{bert_patient_predictions.png}

@@

% Appendix A
% Figure 2 - Overview
\section{Overview}
\begin{figure}[h] \label{app:overview}
\centering 
\includegraphics[scale = 0.60]{APOE_SLAT_Overview_High_Resolution.png}
\caption{Overview}

@@

% Appendix D
\section{Keywords} 
\begin{table}[hbtp] 
\floatconts
{app:keywords}
{\caption{Keywords indicative of Cognitive Impairment}}
\centering
    \begin{tabular}{lcc}
        \toprule
        \bfseries Keyword & \bfseries Match Count \\
        \midrule

        \bfseries Memory & 109218 \\ 
        \bfseries Cognition & 87655 \\ 
        \bfseries Dementia & 51034 \\ 
        \bfseries Cerebral & 45886 \\ 
        \bfseries Cerebrovascular & 36370 \\ 
        \bfseries Cerebellar & 26863 \\
        \bfseries Cognitive Impairment & 20267 \\ 
        \bfseries Alzheimer & 20581 \\ 
        \bfseries MOCA & 9767 \\ 
        \bfseries Neurocognitive & 7711 \\ 
        \bfseries MCI & 3889 \\ 
        \bfseries Amnesia & 3695 \\ 
        \bfseries AD & 2673 \\ 
        \bfseries Lewy & 2561 \\ 
        \bfseries MMSE & 2134 \\ 
        \bfseries LBD & 224 \\ 
        \bfseries Corticobasal & 147 \\ 
        \bfseries Picks & 41 \\

        \bottomrule
        \end{tabular}

\end{table}

% Appendix E
\section{Top TF-IDF Word Features} \label{app:app3}
\begin{table}[hbtp]
    \begin{tabular}{lcccc}
    \toprule 
    \bfseries Word & \bfseries Corr & \bfseries Word & \bfseries Corr \\
    \midrule

    \bfseries Intact &  0.56 & \bfseries Experiences & 0.36 \\
    \bfseries Oriented &  0.43 & \bfseries Associations & 0.36 \\ 
    \bfseries Concentration &  0.42 & \bfseries Homicidal & 0.36 \\ 
    \bfseries Orientation &  0.41 & \bfseries Observation & 0.36 \\
    \bfseries Sensorium &  0.40 & \bfseries Knowledge & 0.36 \\ 
    \bfseries Perceptions &  0.40 & \bfseries Abstract & 0.36 \\
    \bfseries Judgement &  0.39 & \bfseries Suicidal & 0.35 \\
    \bfseries Fund & 0.38 & \bfseries Attention & 0.35 \\
    \bfseries Insight &  0.36 & \bfseries Content & 0.34 \\ 
    \bfseries Ideation &  0.36 & \bfseries Thought & 0.34  \\

    \bottomrule
  \end{tabular}
  {\caption{Top 20 TF-IDF Word Features and their Correlation Coefficient}}
\end{table}

@@

% Table 3 + 4 - Relation of Med/ICD Codes to Model Predictions
% \begin{table*}[hbtp]
% \floatconts
% {tab:table3}
% \centering 
%   {\begin{tabular}{cccccc}
%     \toprule 
%     \bfseries  & \bfseries Count & \bfseries Yes (\%) & \bfseries No/Ntr (\%)  & \bfseries Med/ICD Code (\%)  \\ 
%     \midrule
%     \bfseriesAPOE ${\bm{\varepsilon}}$2} &  1754 &  0.15 &  0.85 &  0.11  \\
%     \bfseriesAPOE ${\bm{\varepsilon}}$3} &  8751 &  0.15 &  0.85 &  0.11  \\
%     \bfseriesAPOE ${\bm{\varepsilon}}$4} &  3436 &  0.18 &  0.82 &  0.17  \\
